---
title: "Wine Quality meetup 20/03/2019"
output: html_notebook
---

```{r}
library(tidyverse)
library(caret)
library(doMC)
library(ggcorrplot)
registerDoMC(cores=7)

```
## Load Datasets
```{r}
winedataset_blanco <- read_csv("blanco_train.csv.gz")
winedataset_red <- read_csv("tinto_train.csv.gz")

winedataset_blanco$type="white"
winedataset_red$type="red"

winedataset<-rbind(winedataset_blanco,winedataset_red)

winedataset
winedataset %>% map(is.null)
```
```{r}
winedataset %>% group_by(quality) %>% summarise(total=n())
winedataset %>% group_by(`total sulfur dioxide`,quality)  %>% summarise(total=n())
```
## Exploratory Analysis
### Correlation Matrix
```{r}
#Matriz de correlacion

cor_matrix<-cor(winedataset %>% select(-type))
ggcorrplot(cor_matrix)
```
### Boxplot volatile
```{r}
ggplot(winedataset)+
  geom_boxplot(aes(x=as.factor(quality),y=`volatile acidity`,fill=as.factor(quality)))
  
```
### Boxplot alcohol
```{r}
ggplot(winedataset)+
  geom_boxplot(aes(x=as.factor(quality),y=`alcohol`))
```
## Create categorical features
```{r eval=FALSE, include=FALSE}
trainset<-winedataset %>% mutate(vinegar = ifelse(`volatile acidity`<=0.4,'low',
                                        ifelse(`volatile acidity`>0.4 & `volatile acidity`<=0.8,'medium',
                                        'high'))) %>%
                          mutate(acohol_level = ifelse(`alcohol`<=9,'low',
                                        ifelse(`alcohol`>9 & `alcohol`<=11,'medium',
                                        'high'))) %>%  select(-`residual sugar`,-`fixed acidity`,-`volatile acidity`,-alcohol,-`free sulfur dioxide`)

#trainset<-winedataset %>% select(`volatile acidity`,density,pH,`residual sugar`,`fixed acidity`,`free sulfur dioxide`,quality)

#ggplot(trainset)+
#         geom_point(aes(x=`free sulfur dioxide`,y=`total sulfur dioxide`))
```

## Create category labels for quality
```{r eval=FALSE, include=FALSE}
set.seed(10)

trainset <- winedataset %>% mutate(quality=ifelse(quality==3,'low',
                                   ifelse(quality==4,'low',
                                   ifelse(quality==5,'medium',
                                   ifelse(quality==6,'medium',
                                   ifelse(quality==7,'high','high'
                                   )))))) #%>% filter(quality %in% c('seven','five','six'))

```
## Create clustering labels (dbscan)
```{r eval=FALSE, include=FALSE}
library(dbscan)


dbscan_mod<-dbscan(trainset %>% select(-quality,-type), eps=5, minPts = 10)
trainset <-cbind(trainset,cluster=dbscan_mod$cluster)
trainset %>% group_by(quality,cluster) %>% summarise(n=n()) %>%
  ggplot()+
    geom_col(aes(x=quality,y=n,fill=as.factor(cluster)))

```

## Create clustering labels (kmeans)
```{r eval=FALSE, include=FALSE}


kmeans_mod<-kmeans(trainset %>% select(-quality,-type),centers =8,nstart=40)
trainset <-cbind(trainset,cluster=kmeans_mod$cluster)
trainset %>% group_by(quality,cluster) %>% summarise(n=n()) %>%
  ggplot()+
    geom_col(aes(y=n,x=as.factor(cluster)))+
  facet_wrap(~quality)

trainset
```


## Eliminate type
```{r}

trainset <- trainset %>% select(-type)
```

```{r}
names(trainset)
```
## Split train and test
```{r}

trainIndex <- createDataPartition(as.factor(trainset$quality), p=0.80, list=FALSE)
data_train <- trainset[ trainIndex,]
data_test <-  trainset[-trainIndex,]
colnames(data_train) <- make.names(colnames(data_train))
colnames(data_test) <- make.names(colnames(data_test))


```
### Plot class distribution in train
```{r}
data_train  %>% group_by(quality) %>% summarise(total=n()) %>%
  ggplot()+
  geom_col(aes(x=quality,y=total,fill=quality))+
  theme_classic()

```
### Plot class distribution in test
```{r}
data_test  %>% group_by(quality) %>% summarise(total=n()) %>%
  ggplot()+
  geom_col(aes(x=quality,y=total,fill=quality))+
  theme_classic()
```
## Feature selection
```{r eval=FALSE, include=FALSE}
rfecrtl <- rfeControl(functions=rfFuncs, method="cv", number=10,allowParallel=TRUE)
results <- rfe(quality~. , data=data_train, sizes=c(1:13), rfeControl=rfecrtl)
results
predictors(results)
# plot the results
plot(results, type=c("g", "o"))
```

## Train model
```{r}
ctrl_fast <- trainControl(method="cv", 
                     repeats=1,
                     number=5, 
                   #  summaryFunction=twoClassSummary,
                     verboseIter=T,
                     classProbs=T,
                     allowParallel = TRUE)  
```

```{r}
data_train %>% filter(quality == 'medium') %>% sample_n(size = 100,replace = TRUE) %>% union(data_train)

ctrl_fast$sampling<-"up"

svmGrid <-  expand.grid(sigma= c(0.001,0.0001,0.00001), 
                        C = c(1,2,4,8,16,32,64,80,100,120) 
                        )

#svmGrid <-  expand.grid(C= c(100), sigma = c(1))


train_formula<-formula(quality~.)
rfFitupsam<- train(train_formula,
               data = data_train,
               #method = "rf",   # Radial kernel
               #method = "xgbTree",
               method = "rf",
               #tuneLength = 9,
               #tuneGrid = svmGrid,
               #preProcess=c("scale","center"),
               #metric="ROC",
               #weights = model_weights,
               trControl = ctrl_fast)

#plot(rfFitupsam)
rfFitupsam
#rfFitupsam$finalModel
```
```{r}
importance <- varImp(rfFitupsam, scale=FALSE)
plot(importance)
```
## Test model
```{r}
predsrfprobsamp=predict(rfFitupsam,data_test)
# use for regresion
#confusionMatrix(as.factor(predsrfprobsamp %>% round()),as.factor(data_test$quality))

confusionMatrix(predsrfprobsamp,as.factor(data_test$quality))

```
```{r}
#confusionmat <- table(predsrfprobsamp %>% round(),as.factor(data_test$quality))

confusionmat <- table(predsrfprobsamp,as.factor(data_test$quality))

confusionmat
reshape2::melt(confusionmat) %>%
  ggplot(aes(x=predsrfprobsamp,y=Var2))+
  geom_tile(aes(fill=value), colour = "white") + 
   geom_text(aes(label = sprintf("%1.0f", value)), vjust = 1)+
  scale_fill_gradient(low = "blue", high = "red")+
  xlab(" Predicted Activity ")+ylab(" Actual Activity")+
  scale_y_discrete(limits=c('low','medium','high'))+
  scale_x_discrete(limits=c('high','medium','low'))+
  
  #scale_y_discrete(limits=c('three','six','seven','four','five','eight'))+
  #scale_x_discrete(limits=c('eight','five','four','seven','six','three'))+
  
  theme_bw()+ theme(legend.position = "none")
```

