---
title: "Introduction To Machine Learning and Deep Learning with R. LAB 1. The Wine Quality dataset"
output: html_notebook
---

```{r}
# For manipulating the datasets
library(dplyr)
library(readr)

# For plotting correlation matrix
library(ggcorrplot)


# Machine Learning library
library(caret)
# For Multi-core processing support
library(doMC)
# Use 3 cores, changet it accordingly. 
registerDoMC(cores=7)

```
# GET THE DATA
## Load the datasets

THE WINE QUALITY DATASET

The two datasets are related to red and white variants of the Portuguese "Vinho Verde" wine. For more details, consult the reference [Cortez et al., 2009]. 
Due to privacy and logistic issues, only physicochemical (inputs) and sensory (the output) variables are available (e.g. there is no data about grape types, wine brand, wine selling price, etc.).

These datasets can be viewed as classification or regression tasks. The classes are ordered and not balanced (e.g. there are much more normal wines than excellent or poor ones).

Available at https://archive.ics.uci.edu/ml/datasets/wine+quality


```{r}
winedataset_blanco <- read_csv("data/blanco_train.csv.gz")
winedataset_red <- read_csv("data/tinto_train.csv.gz")

# Create a new feature for the type 
winedataset_blanco$type="white"
winedataset_red$type="red"

# Merge both datasets into one.
winedataset<-rbind(winedataset_blanco,winedataset_red)



# Print the dataset
winedataset

# Create categories
winedataset <- winedataset %>% mutate(quality=ifelse(quality==3,'low',
                                   ifelse(quality==4,'low',
                                   ifelse(quality==5,'medium',
                                   ifelse(quality==6,'medium',
                                   ifelse(quality==7,'high','high'
                                   ))))))


winedataset %>% group_by(quality) %>% summarise(n=n())
```

# TRAIN THE MODEL
## Split train and test
```{r}


trainIndex <- createDataPartition(as.factor(trainset$quality), p=0.80, list=FALSE)
data_train <- trainset[ trainIndex,]
data_test <-  trainset[-trainIndex,]
colnames(data_train) <- make.names(colnames(data_train))
colnames(data_test) <- make.names(colnames(data_test))
data_train$quality <- as.factor(data_train$quality)
data_test$quality <- as.factor(data_test$quality)

```

## Train model
```{r}

ctrl_fast <- trainControl(method="repeatedcv", 
                       number=5, 
                       repeats = 2,
                     verboseIter=T,
                     classProbs=F,
                     allowParallel = TRUE
                  
                     )  
```

```{r}
registerDoMC(cores=7)
train_formula<-formula(quality~.-pH)

#ctrl_fast$sampling<-"up"

rfFitupsam<- train(train_formula,
               data = data_train,
               #tuneLength=9,
               #method="rpart",
               #method = "rf",
               #method = "knn",
               preProcess=c("scale","center"),
               trControl = ctrl_fast)

rfFitupsam

```
```{r}
importance <- varImp(rfFitupsam, scale=FALSE)
plot(importance)
```

# TEST THE DATA
```{r}
predsrfprobsamp=predict(rfFitupsam,data_test)
as.data.frame(predsrfprobsamp)

confusionMatrix(predsrfprobsamp,as.factor(data_test$quality))
```


```{r}
train_formula<-formula(quality~.)
rfFitupsam<- train(train_formula,
               data = data_train,
               method = "rf",
               #tuneLength = 9,
               #tuneGrid = svmGrid,
               #preProcess=c("scale","center"),
               #metric="ROC",
               #weights = model_weights,
               trControl = ctrl_fast)
```




