---
title: "TidyText analysis"
output: html_notebook
---
```{r}
library(readr)
library(dplyr)
library(tidytext)
```
```{r}
movies_dataset<-read_csv("data/movie-pang02.csv.gz")
glimpse(movies_dataset)
head(movies_dataset)

```
# Bag of Words Tokenisation

In this approach, we represent each word in a document as a token (or feature) and each document as a vector of features. In addition, for simplicity, we disregard word order and focus only on the number of occurrences of each word i.e., we represent each document as a multi-set ‘bag’ of words.


```{r}

dtm<-movies_dataset %>% select(-class)   %>% 
  mutate(row=row_number())  

dtm <- dtm %>% unnest_tokens(word,text) %>% group_by(word,row) %>% summarise(total=n()) %>% cast_sparse(row,word,total)

dtm
str(as.matrix(dtm))
as.matrix(dtm)[1:2,2000:2030] 

```

# Remove Stop Words

```{r}
data(stop_words)
head(stop_words)
movies_dataset<-read_csv("data/movie-pang02.csv.gz")

movies_dataset<-movies_dataset  %>%  mutate(rownumber=row_number()) 

dtm<-movies_dataset %>% select(-class) %>% unnest_tokens(word,text) %>% group_by(word,rownumber) %>% 
  summarise(total=n()) %>%
  anti_join(stop_words)

dtm<- dtm %>% cast_sparse(rownumber,word,total)
dtm<-as.matrix(dtm) %>% as.data.frame()




dtm<-inner_join(movies_dataset,dtm,by=c('row')) %>% select(-text.x)
dtm %>% select(rownumber)
```
```{r}
i
```

# Term frequency
The statistic tf-idf is intended to measure how important a word is to a document in a collection (or corpus) of documents, for example, to one novel in a collection of novels or to one website in a collection of websites. 


```{r}

dtm<-movies_dataset %>% select(-class)  %>% sample_n(100) %>% 
  mutate(row=row_number()) %>% unnest_tokens(word,text) %>% group_by(word,row) %>% 
  summarise(total=n()) %>%
  anti_join(stop_words)
row_words <- dtm%>% count(row,word, sort=TRUE)
total_words <- dtm %>% group_by(row) %>% summarise(total=n())

inner_join(row_words,total_words) %>%   bind_tf_idf(word, row, n)


```


